Concurrent Programming in Harmony

### 2021-02-24 book/paper.tex
Latest

\autoref{fig:tas} goes on to implement mutual exclusion for
a set of \texttt{N} threads.
The approach is called \emph{spinlock},
\index{spinlock}%
because each thread is ``spinning'' (executing a tight loop) until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each thread $i$ is initialized to \texttt{True}.
An important invariant, $\mathcal{I}_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $\mathcal{I}_2(i)$, is that if thread $i$ is executing between
lines $18 \cdots 22$ (which includes the critical section),
then \textit{private}[$i$] == \texttt{False}.
Between the two (i.e., $\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$),
it is clear that only one thread can be in the
critical section at the same time.
For those who read through the previous chapter:
$\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$ is an inductive invariant.

@@

\section{Constants, Global and Local Variables}

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Hartek Sabharwal,
Heather Zheng,
Lorenzo Alvisi,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
William Ma,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

\autoref{fig:tas} goes on to implement mutual exclusion for
a set of \texttt{N} threads.
The approach is called \emph{spinlock},
\index{spinlock}%
because each thread is ``spinning'' (executing a tight loop) until
it can acquire the lock.
The program uses $\mathtt{N}+1$ variables.
Variable \textit{shared} is initialized to \texttt{False} while
\textit{private}[$i$] for each thread $i$ is initialized to \texttt{True}.
Method \texttt{thread} demonstrates how a local variable can be declared
in Harmony using the \textbf{let} statement---the syntax is similar to
\textbf{for} statements.  \autoref{sec:vars} provides further information.
In this case $p$ contains the address of the \textit{private} entry
for the current thread.

An important invariant, $\mathcal{I}_1$, of the program is that at any time at most
one of these variables is \texttt{False}.
Another invariant, $\mathcal{I}_2(i)$, is that if thread $i$ is executing between
lines $18 \cdots 22$ (which includes the critical section),
then \textit{private}[$i$] == \texttt{False}.
Between the two (i.e., $\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$),
it is clear that only one thread can be in the
critical section at the same time.
For those who read through the previous chapter:
$\mathcal{I}_1 \land \forall i: \mathcal{I}_2(i)$ is an inductive invariant.

@@

\section{Constants, Global and Local Variables}\label{sec:vars}

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Hartek Sabharwal,
Heather Zheng,
Lorenzo Alvisi,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
William Ma,
Xiangyu Zhang,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
